---
# title: "Data Quality Check Report"
# author: "Insitute for Alpine Environment, Eurac Research"
output: html_document
params:
    report_mydata:                 # dataframe of data processed
    station_name:           # chr:  name of station where to put input files.
    errors_list_critical:   # list:  list containing status and eventually errors information
    errors_list_warning:    # list:  list containing status and eventually errors information
    errors_list_report_errors:   # list:  list containing status and eventually errors information
    dqc_date:               # date: date DQC
---

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}
mydata <- params$report_mydata
station_name <- params$station_name
errors_list_critical <- params$errors_list_critical
errors_list_warning <- params$errors_list_warning
errors_list_report_errors <- params$errors_list_report_errors
dqc_date <- params$dqc_date
```

## Station: **`r  station_name`**

#### Data Quality Check : **`r  dqc_date`**

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=FALSE}
# names(errors_list_warning)

# names(errors_list_critical)

str(errors_list_critical)
str(errors_list_warning)
str(errors_list_report_errors)


```

<!-- ............... CRITICAL STATUS ICINGA ............... -->

<!-- err_empty -->

##`r if(errors_list_critical$err_empty$Status == "Y"){ paste("File empty!")}`
`r if(errors_list_critical$err_empty$Status == "Y"){ paste("The file of station",station_name, "is empty.")}`

<!-- err_logger_number -->

##`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger wrong number!")}`
`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger numbers doesn't match. Old:",errors_list_critical$err_logger_number$Values[1], "New:",errors_list_critical$err_logger_number$Values[2])}`

<!-- err_structure -->

##`r if(errors_list_critical$err_structure$Status == "Y"){ paste("File wrong structure!")}`
```{r echo=FALSE}
if(errors_list_critical$err_structure$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_structure$Values)
  kable(errors_list_critical$err_structure$Values)
}
```

<!-- err_no_new_data -->

##`r if(errors_list_critical$err_no_new_data$Status == "Y"){ paste("No new data!")}`
<!-- `r if(errors_list_critical$err_no_new_data$Status == "Y"){paste("Date issue! Date in download table is successive of the last date in .dat file")}` -->
`r if(errors_list_critical$err_no_new_data$Status == "Y"){paste("Date issue! Date download table (DT): ",as.character(errors_list_critical$err_no_new_data$Values[1]),". Last date in data file (LT): ",as.character(errors_list_critical$err_no_new_data$Values[2]),". Suggestion: LT should be later than DT", sep="")}`

<!-- err_overlap -->

##`r if(errors_list_critical$err_overlap$Status == "Y"){ paste("Data overlap!")}`
```{r echo=FALSE}
if(errors_list_critical$err_overlap$Status == "Y"){ 
  # df_overlap  = data.frame("overlap:",errors_list_critical$err_overlap$Values)
  # colnames(df_overlap) = c("", "Date")
  df_overlap = errors_list_critical$err_overlap$Values
  # DT::datatable(df_overlap,rownames = F)
  kable(df_overlap,rownames = F)
}
```

<!-- err_missing_record -->

##`r if(errors_list_critical$err_missing_record$Status == "Y"){ paste("Data gap, no record!")}`
```{r echo=FALSE}
if(errors_list_critical$err_missing_record$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_missing_record$Values)
  kable(errors_list_critical$err_missing_record$Values)
}
```

<!-- err_restart_record -->

##`r if(errors_list_critical$err_restart_record$Status == "Y"){ paste("Data gap, restart record!")}`
```{r echo=FALSE}
if(errors_list_critical$err_restart_record$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_restart_record$Values)
  kable(errors_list_critical$err_restart_record$Values)
}
```




<!-- err_date_missing -->

##`r if(errors_list_critical$err_date_missing$Status == "Y"){ paste("Data gap")}`
```{r echo=FALSE, warning=FALSE, results='asis',fig.width= 12,fig.height= 6 }
if(errors_list_critical$err_date_missing$Status == "Y"){ 
  
  time_mydata = as.POSIXct(mydata[, which(colnames(mydata) == "TIMESTAMP")], tz = "Etc/GMT-1")
  
  mydata_df = mydata
  date_filled = ifelse(mydata_df$RECORD != -1,F,T)
  
  date_classification = data.frame(time_mydata, date_filled)
  colnames(date_classification) = c("TIMESTAMP","Classification")
  melt_date_classification = melt(date_classification,id.var = "TIMESTAMP")
  melt_date_classification$variable = rep(0,length(melt_date_classification$variable))
  melt_date_classification$value = as.factor(melt_date_classification$value)
  
  table = errors_list_critical$err_date_missing$Values
  
  table$From = as.POSIXct(as.character(table$From),tz = "Etc/GMT-1")-15*60/2
  table$To = as.POSIXct(as.character(table$To),tz = "Etc/GMT-1")+15*60/2
  
  g0 = ggplot()+
    geom_rect(data = table,aes(xmin = From, xmax = To, ymin = -Inf, ymax = Inf),alpha = 0.25)+
    geom_point(data = melt_date_classification, aes(x = TIMESTAMP, y = variable, colour = value))+
    scale_colour_manual(name = "",values = c("green", "red"))+
    ggtitle(paste("Missing dates"),subtitle = paste(paste("From:",min(melt_date_classification$TIMESTAMP), "to", max(melt_date_classification$TIMESTAMP)),
            paste("Total missing dates:", sum(table$`Number of Record`,na.rm = T),"records - " , 15*sum(table$`Number of Record`,na.rm = T)/60, "hours"),sep = "\n"))+
    scale_x_datetime(date_labels = "%b %d",date_minor_breaks = "1 day") +
    scale_y_continuous(name = "")+
    theme_bw()+
    theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major = element_blank(),
            panel.grid.minor = element_blank())
  
    
  knit_print(g0)

  # print(datatable(errors_list_warning$err_date_missing$Values))
  kable(errors_list_critical$err_date_missing$Values)
}
```

<!-- ............... WARNINGS STATUS ICINGA ............... -->
<!-- err_range_alert -->

##`r if(errors_list_warning$err_range_alert$Status == "Y"){ paste("Data out of range (warnings)!")}`
```{r echo=FALSE, warning=FALSE, results='asis',fig.width= 12,fig.height= 6}
if(errors_list_warning$err_range_alert$Status == "Y"){
  table = errors_list_warning$err_range_alert$Values
  # table$Variable = as.factor(table$Variable)
  vars = unique(table$Variable)

  time_mydata = as.POSIXct(mydata[, which(colnames(mydata) == "TIMESTAMP")], tz = "Etc/GMT-1")

  for(i in 1:length(vars)){
    tab_var_v0 = table[which(table$Variable == vars[i]),]

    tab_var = tab_var_v0
    tab_var$From =  as.POSIXct(tab_var$From,tz = "Etc/GMT-1")-15*60/2
    tab_var$To =  as.POSIXct(tab_var$To,tz = "Etc/GMT-1")+15*60/2
    tab_var$Hours =  as.numeric(tab_var$Hours)

    tab_var$Error = factor(tab_var$Error,levels = c("NaN_value","Too_low","Too_high"))

    mydata_var = mydata[,vars[i]]
    mydata_df = data.frame(time_mydata, mydata_var)
    colnames(mydata_df) = c("TIMESTAMP",vars[i])

    melt_mydata = melt(mydata_df,id.var = "TIMESTAMP")
    melt_mydata$value = as.numeric(melt_mydata$value)
    
    
    g1 = ggplot()+
      geom_rect(data = tab_var,aes(xmin = From, xmax = To, ymin = -Inf, ymax = Inf, fill = Error),alpha = 0.5)+
      geom_line(data = melt_mydata, aes(x = TIMESTAMP, y = value))+
      scale_fill_manual(name = "",values = c("grey20","blue", "red"), labels = c("NaN_value","Too_low","Too_high"),drop = F)+
      ggtitle(paste("Variable:", vars[i]),subtitle = paste(paste("From:",min(melt_mydata$TIMESTAMP), "to", max(melt_mydata$TIMESTAMP)),
                                                           paste("Total NaN:",sum(tab_var$Hours[which(tab_var$Error == "NaN_value")], na.rm = T),"hours"),   # cambiare modo sommare
                                                           paste("Total low data:",sum(tab_var$Hours[which(tab_var$Error == "Too_low")], na.rm = T),"hours"),
                                                           paste("Total high data:",sum(tab_var$Hours[which(tab_var$Error == "Too_high")], na.rm = T),"hours"),sep = "\n"))+
      scale_x_datetime(date_labels = "%b %d",date_minor_breaks = "1 day") +
      scale_y_continuous(name = vars[i])+
      theme_bw()+
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank())

    # d1 = data.frame(c(1,2),c(2,5))
    # colnames(d1) = c("x","y")
    # g1 = ggplot(data = d1, aes(x,y))+geom_point()+geom_line()+ggtitle(vars[i])
    print(g1)

    # print(xtable(tab_var_v0[order(tab_var_v0$From),]),type = "html")
    cat(hwrite(tab_var_v0[order(tab_var_v0$From),], border=0, center=TRUE,  width='1000px', row.names=FALSE, row.style=list('font-weight:bold')))
    # print(kable(tab_var_v0[order(tab_var_v0$From),],row.names = F),type = "html")
    # print( htmltools::tagList(datatable(tab_var_v0[order(tab_var_v0$From),])))
    cat (c("------------------------------------------------------------------------"),sep = "\n")
}


  # kable(errors_list_report_errors$err_out_of_range$Values)
}
```


<!-- ............... REPORT STATUS ............... -->

<!-- err_duplicates_rows -->

<!-- ##`r if(errors_list_report_errors$err_duplicates_rows$Status == "Y"){ paste("WARNING! Station", station_name, "has duplicated rows in .dat file")}` -->

<!-- err_out_of_range -->

##`r if(errors_list_report_errors$err_out_of_range$Status == "Y"){ paste("Data out of physical range!")}`
```{r echo=FALSE, warning=FALSE, results='asis',fig.width= 12,fig.height= 6}
if(errors_list_report_errors$err_out_of_range$Status == "Y"){
  table = errors_list_report_errors$err_out_of_range$Values
  # table$Variable = as.factor(table$Variable)
  vars = unique(table$Variable)

  time_mydata = as.POSIXct(mydata[, which(colnames(mydata) == "TIMESTAMP")], tz = "Etc/GMT-1")

  for(i in 1:length(vars)){
    tab_var_v0 = table[which(table$Variable == vars[i]),]

    tab_var = tab_var_v0
    tab_var$From =  as.POSIXct(tab_var$From,tz = "Etc/GMT-1")-15*60/2
    tab_var$To =  as.POSIXct(tab_var$To,tz = "Etc/GMT-1")+15*60/2
    tab_var$Hours =  as.numeric(tab_var$Hours)

    tab_var$Error = factor(tab_var$Error,levels = c("NaN_value","Too_low","Too_high"))

    mydata_var = mydata[,vars[i]]
    mydata_df = data.frame(time_mydata, mydata_var)
    colnames(mydata_df) = c("TIMESTAMP",vars[i])

    melt_mydata = melt(mydata_df,id.var = "TIMESTAMP")
    melt_mydata$value = as.numeric(melt_mydata$value)
    
    
    g1 = ggplot()+
      geom_rect(data = tab_var,aes(xmin = From, xmax = To, ymin = -Inf, ymax = Inf, fill = Error),alpha = 0.5)+
      geom_line(data = melt_mydata, aes(x = TIMESTAMP, y = value))+
      scale_fill_manual(name = "",values = c("grey20","blue", "red"), labels = c("NaN_value","Too_low","Too_high"),drop = F)+
      ggtitle(paste("Variable:", vars[i]),subtitle = paste(paste("From:",min(melt_mydata$TIMESTAMP), "to", max(melt_mydata$TIMESTAMP)),
                                                           paste("Total NaN:",sum(tab_var$Hours[which(tab_var$Error == "NaN_value")], na.rm = T),"hours"),   # cambiare modo sommare
                                                           paste("Total low data:",sum(tab_var$Hours[which(tab_var$Error == "Too_low")], na.rm = T),"hours"),
                                                           paste("Total high data:",sum(tab_var$Hours[which(tab_var$Error == "Too_high")], na.rm = T),"hours"),sep = "\n"))+
      scale_x_datetime(date_labels = "%b %d",date_minor_breaks = "1 day") +
      scale_y_continuous(name = vars[i])+
      theme_bw()+
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank())

    # d1 = data.frame(c(1,2),c(2,5))
    # colnames(d1) = c("x","y")
    # g1 = ggplot(data = d1, aes(x,y))+geom_point()+geom_line()+ggtitle(vars[i])
    print(g1)

    # print(xtable(tab_var_v0[order(tab_var_v0$From),]),type = "html")
    cat(hwrite(tab_var_v0[order(tab_var_v0$From),], border=0, center=TRUE,  width='1000px', row.names=FALSE, row.style=list('font-weight:bold')))
    # print(kable(tab_var_v0[order(tab_var_v0$From),],row.names = F),type = "html")
    # print( htmltools::tagList(datatable(tab_var_v0[order(tab_var_v0$From),])))
    cat (c("------------------------------------------------------------------------"),sep = "\n")
}







  # kable(errors_list_report_errors$err_out_of_range$Values)
}
```

