---
# title: "Data Quality Check Warning Report"
# author: "Insitute for Alpine Environment, Eurac Research"
output: html_document
params:
    station_name:           # chr:  name of station where to put input files.
    errors_list_critical:   # list:  list containing status and eventually errors information
    # errors_list_warning:    # list:  list containing status and eventually errors information
    dqc_date:               # date: date DQC
---



```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}
station_name <- params$station_name
errors_list_critical <- params$errors_list_critical
# errors_list_critical <- params$errors_list_critical
dqc_date <- params$dqc_date
```

## Station: **`r  station_name`**

##### Data Quality Check : **`r  dqc_date`**

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=FALSE}
# names(errors_list_warning)

# names(errors_list_critical)


```

<!-- ............... CRITICAL STATUS ICINGA ............... -->

<!-- err_empty -->

##`r if(errors_list_critical$err_empty$Status == "Y"){ paste("File empty!")}`
`r if(errors_list_critical$err_empty$Status == "Y"){ paste("The file of station",station_name, "is empty.")}`

<!-- err_logger_number -->

##`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger information changed!")}`
```{r echo=FALSE}
if(errors_list_critical$err_logger_number$Status == "Y"){ 
  # datatable(errors_list_critical$err_structure$Values)
  kable(errors_list_critical$err_logger_number$Values)
}
```

<!-- `r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger numbers doesn't match. Old:",errors_list_critical$err_logger_number$Values[1], "New:",errors_list_critical$err_logger_number$Values[2])}` -->

<!-- err_structure -->

##`r if(errors_list_critical$err_structure$Status == "Y"){ paste("File wrong structure!")}`
```{r echo=FALSE}
if(errors_list_critical$err_structure$Status == "Y"){ 
  # datatable(errors_list_critical$err_structure$Values)
  kable(errors_list_critical$err_structure$Values)
}
```

<!-- err_no_new_data -->

##`r if(errors_list_critical$err_no_new_data$Status == "Y"){ paste("No new data!")}`
`r if(errors_list_critical$err_no_new_data$Status == "Y"){paste("No new data! Date in download table is successive of the last date in .dat file")}`

<!-- err_overlap -->

##`r if(errors_list_critical$err_overlap$Status == "Y"){ paste("Data Overlap!")}`
```{r echo=FALSE, result = 'asis'}
if(errors_list_critical$err_overlap$Status == "Y"){ 
  # df_overlap  = data.frame("overlap:",errors_list_critical$err_overlap$Values)
  # colnames(df_overlap) = c("", "Date")
  df_overlap = errors_list_critical$err_overlap$Values
  # DT::datatable(df_overlap,rownames = F)
  kable(df_overlap,rownames = F)
}
```

<!-- err_missing_record -->

##`r if(errors_list_critical$err_missing_record$Status == "Y"){ paste("Data gap, no record!")}`
```{r echo=FALSE}
if(errors_list_critical$err_missing_record$Status == "Y"){ 
  # datatable(errors_list_critical$err_missing_record$Values)
  kable(errors_list_critical$err_missing_record$Values)
}
```

<!-- err_restart_record -->

##`r if(errors_list_critical$err_restart_record$Status == "Y"){ paste("Data gap, restart record!")}`
```{r echo=FALSE}
if(errors_list_critical$err_restart_record$Status == "Y"){ 
  # datatable(errors_list_critical$err_restart_record$Values)
  kable(errors_list_critical$err_restart_record$Values)
}
```


<!-- ............... WARNINGS STATUS ICINGA ............... -->


<!-- err_date_missing -->

##`r if(errors_list_critical$err_date_missing$Status == "Y"){ paste("Data gap!")}`
```{r echo=FALSE}
if(errors_list_critical$err_date_missing$Status == "Y"){ 
  # datatable(errors_list_warning$err_date_missing$Values)
  kable(errors_list_critical$err_date_missing$Values)
  
}
```


<!-- err_range_alert -->

##`r if(errors_list_critical$err_range_alert$Status == "Y"){ paste("Data overrange!")}`
```{r echo=FALSE}
if(errors_list_critical$err_range_alert$Status == "Y"){ 
  # datatable(errors_list_critical$err_range_alert$Values)
  kable(errors_list_critical$err_range_alert$Values)
}
```

