---
title: "Data Quality Check Report"
author: "Insitute for Alpine Environment, Eurac Research"
output: html_document
params:
    project_dir:
    file: 
    scheduling_dir: 
    report_dir: 
    output_dir:  
    support_dir:     
    write_output:
    RANGE_FILE: 
    DATA_FROM_ROW:                                             # <-- Row number of first data
    HEADER_ROW_NUMBER:                                         # <-- Row number of header
    DATETIME_HEADER:                                # <-- header corresponding to TIMESTAMP
    DATETIME_FORMAT:                          # <-- datetime format. Use only: y -> year, m -> month, d -> day, H -> hour, M -> minute
    DATETIME_SAMPLING: 
    RECORD_HEADER:                                    # <-- header corresponding to RECORD
    start_date:                                # <-- starting date to process file
---

Report start at **`r Sys.time()`**


```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}

# remove(list=ls())
Sys.setenv(TZ='Etc/GMT-1') # sets the environment on italy?s time zone

# ..... Libraries .....................................................................................................................................

# library(devtools)
# install_github("bridachristian/DataQualityCheckEuracAlpEnv")
# library("DataQualityCheckEuracAlpEnv")
# 
# library(zoo)
# library(timeSeries)
# library(knitr)
# library(ggplot2)
# library(dplyr)
# library(plyr)
# library(imputeTS)
# library(reshape2)
# library(kableExtra)
# library(pander)


# .....................................................................................................................................................

# ..... Input section .................................................................................................................................

project_dir <- params$project_dir
scheduling_dir <- params$scheduling_dir                  # <-- schelduling directory: for files to be processed
report_dir <-  params$report_dir                    # <-- report directory: where to put reports and files whith overlaps
output_dir <- params$output_dir                  # <-- output directory: where processed files go
support_dir <- params$support_dir       # <-- support directory: where to read support files

write_output <- params$write_output                                             # if write_output == TRUE => write csv is admitted, if == FALSE not!

FILE <- params$file                                      # <-- Write here the file or the list of file  that you want to analyze!

RANGE_FILE = params$RANGE_FILE

DATA_FROM_ROW <- params$DATA_FROM_ROW                                                # <-- Row number of first data
HEADER_ROW_NUMBER <- params$HEADER_ROW_NUMBER                                          # <-- Row number of header
DATETIME_HEADER <- params$DATETIME_HEADER                               # <-- header corresponding to TIMESTAMP
DATETIME_FORMAT <- params$DATETIME_FORMAT                           # <-- datetime format. Use only: y -> year, m -> month, d -> day, H -> hour, M -> minute
DATETIME_SAMPLING <- params$DATETIME_SAMPLING
RECORD_HEADER <- params$RECORD_HEADER                                   # <-- header corresponding to RECORD

start_date <- params$start_date                                 # <-- starting date to process file

myscript <-  paste(project_dir,"Main_script/DQC_Script.R",sep = "")
# read_chunk(myscript)

```

```{r cache=FALSE}

knitr::read_chunk(myscript)

```

```{r test-a}

```

### INPUT info: 

File selected: **`r  FILE`** 

You have also select these parameters:

+ Data start from row: *`r DATA_FROM_ROW`*
+ The name of column is on row: *`r HEADER_ROW_NUMBER`*
+ The datetime header is: *`r DATETIME_HEADER`*
+ The record header is: *`r RECORD_HEADER`*
+ The datetime format is: *`r DATETIME_FORMAT`*
+ The sampling interval is: *`r DATETIME_SAMPLING`*

The folders are: 

+ Data folder: *`r scheduling_dir`*
+ Report folder: *`r report_dir`*
+ Output folder: *`r output_dir`*
+ Support folder: *`r support_dir`*

Range file in support folder is called: *`r RANGE_FILE`* 

You decide:  *`r if(write_output == TRUE){paste("to write output file in output folder")} else{paste(("to don't write output file in output folder"))} `* 


### OUTPUT: 

#### Info empty file:

`r if(flag_empty == 1){paste("Error:", FILE,"without observation")}else{paste(FILE, "has some obseravtion.")}`

#### **Duplicated rows**

More details on: `r paste(output_dir,"Duplicated_",substring(FILE,1,nchar(FILE)-4),".csv",sep = "")`

#### **Overlap**

`r if(flag_overlap == 1){paste("In file:", FILE, " there are the following ovelap:")}else{paste("In", FILE, "there isn't any overlap!")}`


```{r echo=FALSE}
if(flag_overlap == 1){
  # kable(overlap, format = "markdown",align = "c")
  kable(overlap, format = "html",align = "c",row.names = F)%>%
    kable_styling() %>%
    scroll_box( height = "200px") 
  
}

```

#### **Missing dates**

```{r echo=FALSE, warning=FALSE}
if(flag_overlap == 0){
  w = which(colnames(mydata) == DATETIME_HEADER)
  time_tot <- mydata[,w]
  time_tot <- as.POSIXct(time_tot, format = "%Y-%m-%d %H:%M:%S")
  time_missing <- missing_index_date[,2]
  
  df_missing <- data.frame(time_tot,rep("Dates in original file",times = length(time_tot)))
  colnames(df_missing) = c("time","Status")
  df_missing[which(time_tot %in% time_missing ),2] = "Missing dates filled"
  y = rep(1, times = length(time_tot))
  
  Status_num = rep(1,times = length(time_tot))
  Status_num[which(time_tot %in% time_missing )] = 0
  
  df_missing = cbind(df_missing, y,Status_num)
  
  
  theme_new = theme_bw()+theme(axis.title.y=element_blank(),
                               axis.text.y=element_blank(),
                               axis.ticks.y=element_blank(),
                               axis.text.x = element_text(angle = 90, hjust = 1))
  
  
  ggplot(df_missing,aes(x = time, y=y ,colour = Status)) +  
    geom_point(aes(size = Status,shape = Status) )+
    scale_colour_manual(values = c("#7CAE00","#F8766D"))+ 
    scale_shape_manual(values = c(20,124))+
    # scale_x_datetime(name = DATETIME_HEADER,date_breaks = "2 weeks" )+
    theme_new+
    ggtitle("Time distribution of missing dates")
}

```


Statistics of missing dates:

```{r echo=FALSE}
if(flag_overlap == 0){
  Status_num_NA=df_missing
  Status_num_NA = Status_num_NA[,-c(2,3)]
  
  differ = c(0,diff(Status_num_NA$Status_num))
  start = which(differ == -1)
  end  = which(differ == 1) - 1
  gap_lenght = end - start + 1
  
  date_start = Status_num_NA$time[start]
  date_end = Status_num_NA$time[end]
  
  statistic_missing = data.frame(date_start,date_end,gap_lenght)
  colnames(statistic_missing) = c("From", "To", "Number of Record")
  
  # kable(statistic_missing, format = "markdown",align = "c")
  kable(statistic_missing, format = "html",align = "c",row.names = F)%>%
    kable_styling() %>%
    scroll_box( height = "200px") 
}
```

#### **Values out of admitted range**

```{r echo=FALSE, warning=FALSE,results='asis'}
if(flag_overlap == 0){
  for(j in 1:ncol(check_out_of_range)){
    if(colnames(check_out_of_range)[j] ==  DATETIME_HEADER){}else{
      
      # ~~~~~~ preparation data for ggplot ~~~~~~ 
      
      df_tmp = check_out_of_range[,c(which(colnames(check_out_of_range)==DATETIME_HEADER), j)]
      df_factor = df_tmp
      
      df_factor[,2]=as.character(df_factor[,2])
      
      y = rep(1,times = nrow(df_factor))
      df_factor = cbind(df_factor,y)
      colnames(df_factor) = c("time", "Variable", "y") 
      df_factor$y[which(df_factor$Variable == -1)] = 0.9
      df_factor$y[which(df_factor$Variable == 1)] = 1.1
      # colnames(df_factor) =c("time","Variable","y")
      
      # ~~~~~~ preparation data for statistic table ~~~~~~ 
      
      c_oor = colnames(check_out_of_range)[j]
      
      df_oor = check_out_of_range[,c(which(colnames(check_out_of_range)==DATETIME_HEADER), j)]
      colnames(df_oor)= c("time", "variable")
      
      over_range = rep(0, times = nrow(df_oor))
      
      if(length(which(df_oor$variable == 1)) != 0){
        over_range[which(df_oor$variable == 1)] = 1
      }
      
      under_range = rep(0, times = nrow(df_oor))
      
      if(length(which(df_oor$variable == -1)) != 0){
        under_range[which(df_oor$variable == -1)] = 1
      }
      
      df_oor2 = data.frame(df_oor$time, under_range, over_range)
      
      diff_df = cbind(df_oor$time,as.data.frame(rbind(c(0,0),apply(df_oor2[,-1],2, diff))))
      
      if(any(unique(df_oor[,2])!= 0)){
        
        # ~~~~~~ preparation data for ggplot ~~~~~~ 
        
        theme_new2 = theme_bw()+theme(axis.title.y=element_blank(),
                                      axis.text.y=element_blank(),
                                      axis.ticks.y=element_blank(),
                                      axis.text.x = element_text(angle = 90, hjust = 1),
                                      legend.title = element_blank())
        
        # p2 = ggplot(melt_df_ggplot, aes(y=variable, x=time))+
        #   geom_tile(aes(fill = value))+
        #   scale_fill_manual(values = c("green", "red", "red"))
        # 
        # p2
        
        set_limits = data.frame(as.POSIXct(c(df_factor$time[1], df_factor$time[nrow(df_factor)%/%2], df_factor$time[nrow(df_factor)])), c(-1,0,1), c(0,0,0))
        colnames(set_limits) = colnames(df_factor)
        
        df_factor = rbind(df_factor,set_limits)
        
        df_factor$Variable = factor(df_factor$Variable, ordered = TRUE)
        df_factor$Variable <- factor( df_factor$Variable, levels=rev(levels( df_factor$Variable)))
        
        
        p1 = ggplot(df_factor,aes(x = time, y = y,colour = Variable))+
          geom_point(aes(size = Variable,shape = Variable ))+
          scale_colour_manual(values = c("#0000FF","#7CAE00","#F8766D"),labels = c("Above upper limit", "In the range","Below lower limit"))+ 
          scale_shape_manual(values = c(124,20,124),labels =c("Above upper limit", "In the range","Below lower limit"))+
          scale_size_manual(values = c(10,1,10),labels = c("Above upper limit", "In the range","Below lower limit"))+
          scale_x_datetime(name = DATETIME_HEADER,date_breaks = "2 weeks" )+
          theme_new2 +
          ggtitle(colnames(check_out_of_range)[j])+
          scale_y_continuous(limits = c(0.7,1.3))
        
        print(p1)
        
        # ~~~~~~ preparation data for statistic table ~~~~~~ 
        
        under_start_oor = which(diff_df$under_range == 1)
        under_end_oor  = which(diff_df$under_range == -1) - 1
        
        
        if(length(under_start_oor) != 0 & length(under_end_oor) != 0){
          if(under_end_oor[1] < under_start_oor[1]){
            under_start_oor = c(1,under_start_oor)
          }
          if(under_start_oor[length(under_start_oor)] > under_end_oor[length(under_end_oor)] ){
            under_end_oor = c(under_end_oor,nrow(diff_df))
          }
        }
        
        under_gap_lenght_oor = under_end_oor - under_start_oor + 1
        under_date_start_oor = df_oor[under_start_oor,1]
        under_date_end_oor = df_oor[under_end_oor,1]
        
        under_statistic_oor = data.frame(rep("Under lower limit", times = length(under_date_start_oor)), under_date_start_oor,under_date_end_oor,under_gap_lenght_oor)
        colnames(under_statistic_oor) = c(" ","From", "To", "Number of Record")
        
        # over
        
        over_start_oor = which(diff_df$over_range == 1)
        over_end_oor  = which(diff_df$over_range == -1) - 1
        
        
        if(length(over_start_oor) != 0 & length(over_end_oor) != 0){
          if(over_end_oor[1] < over_start_oor[1]){
            over_start_oor = c(1,over_start_oor)
          }
          if(over_start_oor[length(over_start_oor)] > over_end_oor[length(over_end_oor)] ){
            over_end_oor = c(over_end_oor,nrow(diff_df))
          }
        }
        
        over_gap_lenght_oor = over_end_oor - over_start_oor + 1
        over_date_start_oor = df_oor[over_start_oor,1]
        over_date_end_oor = df_oor[over_end_oor,1]
        
        
        over_statistic_oor = data.frame(rep("Above upper limit", times = length(over_date_start_oor)), over_date_start_oor,over_date_end_oor,over_gap_lenght_oor)
        colnames(over_statistic_oor) = c(" ","From", "To", "Number of Record")
        
        
        if(nrow(under_statistic_oor) == 0){
          statistic_oor = over_statistic_oor
        }else{ 
          if(nrow(over_statistic_oor) == 0){
            statistic_oor = under_statistic_oor
          }else{
            statistic_oor= rbind(under_statistic_oor,over_statistic_oor)
          }
        }
        
        
        statistic_oor = statistic_oor[order(statistic_oor$From),] 
        
        # cat(paste("Statistics of data out of range:",c_oor))
        print(kable(statistic_oor, format = "html",align = "c",row.names = F)%>%
                kable_styling() %>%
                scroll_box( height = "200px") ) 
        
      }
    }
  }
  
}

```

Report end at **`r Sys.time()`**

