---
title: "Data Quality Check Warning Report"
author: "Insitute for Alpine Environment, Eurac Research"
output: html_document
params:
    station_name:           # chr:  name of station where to put input files.
    errors_list_critical:   # list:  list containing status and eventually errors information
    errors_list_warning:    # list:  list containing status and eventually errors information
    dqc_date:               # date: date DQC
---



```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}
station_name <- params$station_name
errors_list_critical <- params$errors_list_critical
errors_list_warning <- params$errors_list_warning
dqc_date <- params$dqc_date
```

### Station: **`r  station_name`**

### Data Quality Check : **`r  dqc_date`**

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}
names(errors_list_warning)
errors_list_critical$err_logger_number$Values
```

<!-- err_empty -->

##`r if(errors_list_critical$err_empty$Status == "Y"){ paste("CRITICAL ERROR!")}`
`r if(errors_list_critical$err_empty$Status == "Y"){ paste("The file of station",station_name, "is empty.")}`

<!-- err_logger_number -->

##`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("CRITICAL ERROR!")}`
`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger numbers doesn't match. Old:",errors_list_critical$err_logger_number$Values[1], "New:",errors_list_critical$err_logger_number$Values[2])}`

<!-- err_structure -->

##`r if(errors_list_critical$err_structure$Status == "Y"){ paste("CRITICAL ERROR!")}`
```{r echo=FALSE}
if(errors_list_critical$err_structure$Status == "Y"){ 
DT::datatable(errors_list_critical$err_structure$Values)
}
```

<!-- add -->
<!-- add -->
<!-- add -->
<!-- add -->
<!-- add -->
<!-- add -->


<!-- err_range_alert -->

##`r if(errors_list_warning$err_range_alert$Status == "Y"){ paste("WARNING ERROR!")}`
```{r echo=FALSE}
if(errors_list_warning$err_range_alert$Status == "Y"){ 
DT::datatable(errors_list_warning$err_range_alert$Values)
}
```

