---
title: "Data Quality Check Report"
author: "Insitute for Alpine Environment, Eurac Research"
output: html_document
params:
    report_mydata:                 # dataframe of data processed
    station_name:           # chr:  name of station where to put input files.
    errors_list_critical:   # list:  list containing status and eventually errors information
    errors_list_warning:    # list:  list containing status and eventually errors information
    errors_list_report_errors:   # list:  list containing status and eventually errors information
    dqc_date:               # date: date DQC
---

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=TRUE}
mydata <- params$report_mydata
station_name <- params$station_name
errors_list_critical <- params$errors_list_critical
errors_list_warning <- params$errors_list_warning
errors_list_report_errors <- params$errors_list_report_errors
dqc_date <- params$dqc_date
```

### Station: **`r  station_name`**

### Data Quality Check : **`r  dqc_date`**

```{r message=FALSE,echo=FALSE, warning=FALSE, error=FALSE, eval=FALSE}
# names(errors_list_warning)

# names(errors_list_critical)

str(errors_list_critical)
str(errors_list_warning)
str(errors_list_report_errors)


```

<!-- ............... CRITICAL STATUS ICINGA ............... -->

<!-- err_empty -->

##`r if(errors_list_critical$err_empty$Status == "Y"){ paste("CRITICAL ERROR! Empty file!")}`
`r if(errors_list_critical$err_empty$Status == "Y"){ paste("The file of station",station_name, "is empty.")}`

<!-- err_logger_number -->

##`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("CRITICAL ERROR! Logger number doesn't match")}`
`r if(errors_list_critical$err_logger_number$Status == "Y"){ paste("Logger numbers doesn't match. Old:",errors_list_critical$err_logger_number$Values[1], "New:",errors_list_critical$err_logger_number$Values[2])}`

<!-- err_structure -->

##`r if(errors_list_critical$err_structure$Status == "Y"){ paste("CRITICAL ERROR! Datatable structure issues!")}`
```{r echo=FALSE}
if(errors_list_critical$err_structure$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_structure$Values)
  kable(errors_list_critical$err_structure$Values)
}
```

<!-- err_date_issue -->

##`r if(errors_list_critical$err_date_issue$Status == "Y"){ paste("CRITICAL ERROR! Date issues!")}`
<!-- `r if(errors_list_critical$err_date_issue$Status == "Y"){paste("Date issue! Date in download table is successive of the last date in .dat file")}` -->
`r if(errors_list_critical$err_date_issue$Status == "Y"){paste("Date issue! Date download table (DT): ",as.character(errors_list_critical$err_date_issue$Values[1]),". Last date in data file (LT): ",as.character(errors_list_critical$err_date_issue$Values[2]),". Suggestion: LT should be later than BT", sep="")}`

<!-- err_overlap -->

##`r if(errors_list_critical$err_overlap$Status == "Y"){ paste("CRITICAL ERROR! Overlap!")}`
```{r echo=FALSE}
if(errors_list_critical$err_overlap$Status == "Y"){ 
  df_overlap  = data.frame("overlap:",errors_list_critical$err_overlap$Values)
  colnames(df_overlap) = c("", "Date")
  # DT::datatable(df_overlap,rownames = F)
  kable(df_overlap,rownames = F)
}
```

<!-- err_missing_record -->

##`r if(errors_list_critical$err_missing_record$Status == "Y"){ paste("CRITICAL ERROR! Missing record!")}`
```{r echo=FALSE}
if(errors_list_critical$err_missing_record$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_missing_record$Values)
  kable(errors_list_critical$err_missing_record$Values)
}
```

<!-- err_restart_record -->

##`r if(errors_list_critical$err_restart_record$Status == "Y"){ paste("CRITICAL ERROR! Missing record before a restart!")}`
```{r echo=FALSE}
if(errors_list_critical$err_restart_record$Status == "Y"){ 
  # DT::datatable(errors_list_critical$err_restart_record$Values)
  kable(errors_list_critical$err_restart_record$Values)
}
```


<!-- ............... WARNINGS STATUS ICINGA ............... -->


<!-- err_date_missing -->

##`r if(errors_list_warning$err_date_missing$Status == "Y"){ paste("ERROR! Missing dates!")}`
```{r echo=FALSE, warning=FALSE, results='asis'}
if(errors_list_warning$err_date_missing$Status == "Y"){ 
  
  time_mydata = as.POSIXct(mydata[, which(colnames(mydata) == "TIMESTAMP")], tz = "Etc/GMT-1")
  
  mydata_df = mydata
  date_filled = ifelse(mydata_df$RECORD != -1,F,T)
  
  date_classification = data.frame(time_mydata, date_filled)
  colnames(date_classification) = c("TIMESTAMP","Classification")
  melt_date_classification = melt(date_classification,id.var = "TIMESTAMP")
  melt_date_classification$variable = rep(0,length(melt_date_classification$variable))
  melt_date_classification$value = as.factor(melt_date_classification$value)
  
  table = errors_list_warning$err_date_missing$Values
  
  table$From = as.POSIXct(as.character(table$From),tz = "Etc/GMT-1")
  table$To = as.POSIXct(as.character(table$To),tz = "Etc/GMT-1")
  
  
  
  
  
  
  g1 = ggplot()+
    geom_rect(data = table,aes(xmin = From, xmax = To, ymin = -Inf, ymax = Inf),alpha = 0.25)+
    geom_point(data = melt_date_classification, aes(x = TIMESTAMP, y = variable, colour = value))+
    scale_colour_manual(values = c("green", "red"))
  # +
  #   scale_fill_manual(name = "",values = c("grey20","blue", "red"), labels = c("NaN_value","Too_low","Too_high"),drop = F)+
  #   ggtitle(paste("Variable:", vars[i]),subtitle = paste("From:",min(melt_mydata$TIMESTAMP), "to", max(melt_mydata$TIMESTAMP)))+
  #   scale_x_datetime(date_labels = "%b %d",date_minor_breaks = "1 day") +
  #   theme_bw()
  
  # DT::datatable(errors_list_warning$err_date_missing$Values)
  kable(errors_list_warning$err_date_missing$Values)
}
```


<!-- ............... REPORT STATUS ............... -->
#### Da finire! ristrutturare!
##`r if(errors_list_report_errors$err_out_of_range$Status == "Y"){ paste("ERROR! Values out of physical range!")}`
```{r echo=FALSE, warning=FALSE, results='asis'}
if(errors_list_report_errors$err_out_of_range$Status == "Y"){ 
  table = errors_list_report_errors$err_out_of_range$Values
  # table$Variable = as.factor(table$Variable)
  vars = unique(table$Variable)
  
  time_mydata = as.POSIXct(mydata[, which(colnames(mydata) == "TIMESTAMP")], tz = "Etc/GMT-1")
  
  for(i in 1:length(vars)){
    
    tab_var_v0 = table[which(table$Variable == vars[i]),]
    
    tab_var = tab_var_v0
    tab_var$From =  as.POSIXct(tab_var$From,tz = "Etc/GMT-1")
    tab_var$To =  as.POSIXct(tab_var$To,tz = "Etc/GMT-1")
    # tab_var$Error =  as.factor(tab_var$Error)
    
    tab_var$Error = factor(tab_var$Error,levels = c("NaN_value","Too_low","Too_high"))
    
    mydata_var = mydata[,vars[i]]
    mydata_df = data.frame(time_mydata, mydata_var)
    colnames(mydata_df) = c("TIMESTAMP",vars[i])
    
    melt_mydata = melt(mydata_df,id.var = "TIMESTAMP")
    
    g1 = ggplot()+
      geom_rect(data = tab_var,aes(xmin = From, xmax = To, ymin = -Inf, ymax = Inf, fill = Error),alpha = 0.25)+
      geom_line(data = melt_mydata, aes(x = TIMESTAMP, y = value))+
      scale_fill_manual(name = "",values = c("grey20","blue", "red"), labels = c("NaN_value","Too_low","Too_high"),drop = F)+
      ggtitle(paste("Variable:", vars[i]),subtitle = paste("From:",min(melt_mydata$TIMESTAMP), "to", max(melt_mydata$TIMESTAMP)))+
      scale_x_datetime(date_labels = "%b %d",date_minor_breaks = "1 day") +
      theme_bw()
    
    # d1 = data.frame(c(1,2),c(2,5))
    # colnames(d1) = c("x","y")
    # g1 = ggplot(data = d1, aes(x,y))+geom_point()+geom_line()+ggtitle(vars[i])
    print(g1)
    
    print(kable(tab_var[order(tab_var$From),]),type = "html",include.rownames=FALSE)
    # print(xtable(tab_var_v0[order(tab_var_v0$From),]),type = "html",include.rownames=FALSE)
    
  }
  
  
  
  
  
  
  
  # kable(errors_list_report_errors$err_out_of_range$Values)
}
```
